---
title: "Slide-4"
author: "Carson Drake"
date: "10/14/2018"
output:
  html_document: default
---

```{r setup, include=FALSE}
library(highcharter);
knitr::opts_chunk$set(echo = TRUE);


```

## State with most alcoholic beer? Median graphs, greatest ABV?

Below is an interactive state map that allows you to toggle over each state and
showcase the ABV corresponding to that particular state. It also includes a
heatmap to represent the ABV by color. The lighter the state, the smaller the
ABV. The darker the state, the more higher the ABV. #hcmap is an API that uses
map data from the highcharter. We are calling and leveraging that API in order
to create the graph below. More information on this API can be found at:
http://jkunst.com/highcharter/highmaps.html


```{r}

hcmap("countries/us/us-all", data = StateSummary, value = "medianABV",
	  joinBy = "hc-a2", name = "State Summary | Median ABV",
	  dataLabels = list(enabled = TRUE, format = '{point.name}'),
	  borderColor = "#FAFAFA", borderWidth = 0.1,
	  tooltip = list(valueDecimals = 5,valueSuffix = " ABV")) %>%
	hc_colorAxis(minColor = "#FFFFFF", maxColor = "#34675C") %>%
	hc_mapNavigation(enabled = TRUE) %>%
	hc_title(text = "<b>Median ABV by State</b>",
			 margin = 20, align = "center",
			 style = list(color = "#000000",
			 			 useHTML = TRUE)) %>%
	hc_colorAxis(minColor = "#FFFFFF", maxColor = "#FF0000")

```

